---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
library(ggplot2)
library(dplyr)
```

### A good plot must have labels for its x- and y-axis

After you draw a plot, such as the plot below.

```{r}
diamonds %>%
  ggplot(aes(x = carat, y = price)) +
  geom_point(alpha = 0.5)
```

Readers can be confused because the plot does not have any title or labels.

They may have some questions about the plot:

* What is this plot about?
* What are x-axis measures?
* Which currency is used for price measurement?

So, if we add title and labels to the plot, is the plot more readable? You can know more about the `labs()` by entering `?labs()` in your R console.

```{r}
diamonds %>%
  ggplot(aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  labs(title = "Prices of round cut diamonds", # plot title
       x = "Weight of the diamond (carat)", # x-axis label
       y = "Price (USD)") # y-axis label
```


### Let's have one simple exercise, and remember to give your future plots labels and titles


Try to fill in the blanks.
